Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-06-21 ref_response.tex
Updates from Overleaf

Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitors of SNe Ia is yet to be confirmed. While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014,Ruiter2020} for reviews). The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Kashi2011,Ilkov2012}.

@@

The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia. However, finding self-consistent progenitor and explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult. In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs (linked strongly with the SD scenario but also with many DD scenarios) find difficulty in reproducing the light curves of "normal" SNe Ia as well as "peculiar" objects (\citealt{Ropke2007,Sim2013,Blondin2017}; see \citealt{Maoz2014,Jha2019} for overviews). In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations (primarily related to a DD scenario) has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}. An additional factor in support of the sub-$M_{\mathrm{Ch}}$ model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}. Other proposed scenarios include hybrid models in which standard CO WDs merge with hybrid helium-CO WDs \citep{Zenati2019,Perets2019}. With many models showing promising similarities to observations but each subject to its own drawbacks, it is becoming accepted that more than one progenitor scenario may contribute significantly to the overall population of "normal" SNe Ia; detailed observations are thus required in order to place constraints on the relative fractions of each possible progenitor channel.

>>>>

Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitors of SNe Ia is yet to be confirmed. While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014,Ruiter2020} for reviews). The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Kashi2011,Ilkov2011}.

@@

The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia. However, finding self-consistent progenitor and explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult. In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs (linked strongly with the SD scenario but also with many DD scenarios) find difficulty in reproducing the light curves of "normal" SNe Ia as well as "peculiar" objects (\citealt{Ropke2007,Sim2013,Blondin2017}; see \citealt{Maoz2014,Jha2019} for overviews). In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations (primarily related to a DD scenario) has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}. An additional factor in support of the sub-$M_{\mathrm{Ch}}$ model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}. Other proposed scenarios include hybrid models in which standard CO WDs merge with hybrid helium-CO WDs \citep{Zenati2019}. With many models showing promising similarities to observations but each subject to its own drawbacks, it is becoming accepted that more than one progenitor scenario may contribute significantly to the overall population of "normal" SNe Ia; detailed observations are thus required in order to place constraints on the relative fractions of each possible progenitor channel.
